
\documentclass[
	11pt
]{resume}

\usepackage{geometry}
\usepackage{hyperref}

\name{Alex Lux}

\begin{document}
\noindent
{\fontsize{8}{10}\selectfont
  \href{mailto:alexlux@live.com}{\texttt{alexlux@live.com}} \quad|\quad
  \texttt{(805)\,279-5912}           \quad|\quad
  \href{https://www.alexflux.com/}{\texttt{Portfolio: alexflux.com}} \quad|\quad
  \href{https://www.linkedin.com/in/alex-lux/}{\texttt{linkedin.com/in/alex-lux}} \quad|\quad
  \href{https://github.com/alexlux58}{\texttt{github.com/alexlux58}}
}

\begin{rSection}{Experience}

\begin{rSubsection}{Sohonet}{June 2024 -- Present}{Network Engineer}{Los Angeles, CA}
    \item Manage and optimize a global hybrid network infrastructure connecting film and media production studios across multiple continents, ensuring high availability and resilient connectivity.
    \item Configure and troubleshoot a diverse array of network devices (Cisco, Arista, Aruba, Ruckus, Fortinet, Juniper, Palo Alto, UniFi, Xirrus Wi-Fi), supporting a multi-vendor L2/L3 environment.
    \item Administer network security using next-gen firewalls and VPNs, implementing secure site-to-site and remote VPNs with authentication via RADIUS/LDAP.
    \item Automated network configuration management with Bash/Python scripts, Nautobot templates and Ansible playbooks, supporting 100+ switches and routers.
    \item Integrated AWS cloud networking with on-prem infrastructure using VPNs and Direct Connects; managed DNS and routing for seamless hybrid connectivity.
    \item Monitored network health using SNMP, NetFlow, Grafana and ELK stack; responded to incidents and performed root cause analysis.
    \item Collaborated with cross-functional teams and external vendors to document topologies, standards, and SOPs in NetBox and internal Wikis.
    \item Participate in a 24x7 on-call rotation and be available for after-hour support.
     \item Maintain SaaS applications and troubleshoot network performance issues.

\end{rSubsection}

    \begin{rSubsection}{Tangerine Global}{June 2022 -- June 2024}{Operations/Network Support Engineer}{Simi Valley, CA}
    \item Supported IPTV infrastructure and services, including A/V encoder and decoder troubleshooting across commercial and residential deployments.
    \item Managed over 120 Windows Server VMs used for IPTV delivery; performed regular patching and maintenance to ensure optimal performance.
    \item Monitored network and system health using Zabbix, enabling proactive issue detection and service uptime.
    \item Troubleshot and maintained Layer 2/3 switching and routing, including VLANs, multicast traffic, and QoS optimization.
    \item Diagnosed and repaired coaxial, MoCA, and fiber network connectivity issues across IPTV access networks.
    \item Administered Active Directory—managed users, security groups, and group policies to maintain a secure and efficient IT environment.
    \item Installed and configured Interel Zigbee-based smart home systems for hospitality and residential environments.

\end{rSubsection}

\begin{rSubsection}{Clover Visual Communications LLC}{September 2017 -- May 2022}{IT Associate}{Westlake Village, CA}
      \item Served as the primary IT support for a fast-paced creative agency, supporting both Windows and macOS environments to ensure high uptime and productivity.
    \item Delivered hands-on desktop support: installed, updated, and configured software including Adobe Creative Suite and Microsoft Office.
    \item Troubleshot hardware issues for desktops, laptops, monitors, and peripherals; performed preventative maintenance to extend hardware lifespan.
    \item Assisted with LAN and Wi-Fi troubleshooting—resolving DNS, DHCP, and IP conflicts to maintain seamless network access.
    \item Installed and configured office printers and scanners; resolved print queue and driver issues for both Windows and Mac users.
    \item Provided user training and support, communicating solutions clearly and promoting best practices in security and performance.

\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Skills}
\begin{itemize}
  \item \textbf{Networking:} TCP/IP, BGP, OSPF, IS-IS, VLANs, STP, VPNs (IPsec, SSL, OpenVPN), DHCP, DNS, QoS, SD-WAN, NetBox/Nautobot
  \item \textbf{Security:} FortiGate, Palo Alto, Cisco ASA/FTD, Firewall Policies, VPN Gateways, LDAP, RADIUS, TACACS+, OS patching, hardening
  \item \textbf{Cloud \& Infrastructure:} AWS (VPC, Direct Connect, Route 53), Azure AD, Hybrid Networking, DNS administration, Load Balancers
  \item \textbf{Automation \& Tools:} Python, Bash, PowerShell, Ansible, Git, Jenkins, Docker, Infrastructure as Code, Kubernetes
  \item \textbf{Monitoring \& Logging:} Grafana, Zabbix, Prometheus, SNMP, NetFlow, tcpdump, log parsing
  \item \textbf{Vendors \& Platforms:} Cisco, Juniper, Arista, Fortinet, Palo Alto, Aruba, Ruckus, UniFi, HP, Xirrus
  \item \textbf{Operating Systems:} Linux (Ubuntu, Debian, RHEL), Windows Server, macOS
\end{itemize}
\end{rSection}

\begin{rSection}{Certifications}
    \textbf{Amazon AWS Advanced Networking} \hfill \textit{Expected September 2025} \\
    \textbf{Amazon AWS Security} \hfill \textit{Expected October 2025} \\
    \textbf{CompTIA Linux+} \hfill \textit{2025} \\ 
    \textbf{Cisco CCNA} \hfill \textit{2024} \\
    \textbf{CompTIA Security+} \hfill \textit{2024} \\
\end{rSection}

\begin{rSection}{Education}
	\textbf{California State University Channel Islands, Camarillo, CA} \hfill \textit{August 2020 - May 2022} \\ 
	B.S. in Computer Science \\

    \textbf{Moorpark College, Moorpark, CA} \hfill \textit{August 2017 - May 2020} \\ 
	A.S. in Computer Science and Mathematics \\
\end{rSection}

\end{document}
